\documentclass[8pt,landscape,a4paper]{article}
\usepackage{multicol}
\usepackage{calc}
\usepackage{ifthen}
\usepackage[landscape]{geometry}
\usepackage{amsmath,amsthm,amsfonts,amssymb}
\usepackage{color,graphicx}
\usepackage{hyperref}
\usepackage{tabularx}

\pdfinfo{
  /Title (qstar-cheatsheet.pdf)
  /Creator (TeX)
  /Producer (pdfTeX 1.40.0)
  /Author (Florian Stinglmayr, Johannes Zwirchmayr)
  /Subject (Cheatsheet for qstar)
  /Keywords (pdflatex, latex,pdftex,tex)}

\ifthenelse{\lengthtest { \paperwidth = 11in}}
    { \geometry{top=.5in,left=.5in,right=.5in,bottom=.5in} }
    {\ifthenelse{ \lengthtest{ \paperwidth = 297mm}}
        {\geometry{top=1cm,left=1cm,right=1cm,bottom=1cm} }
        {\geometry{top=1cm,left=1cm,right=1cm,bottom=1cm} }
    }

\pagestyle{empty}

\makeatletter
\renewcommand{\section}{\@startsection{section}{1}{0mm}%
                                {-1ex plus -.5ex minus -.2ex}%
                                {0.5ex plus .2ex}%x
                                {\normalfont\large\bfseries}}
\renewcommand{\subsection}{\@startsection{subsection}{2}{0mm}%
                                {-1ex plus -.5ex minus -.2ex}%
                                {0.5ex plus .2ex}%
                                {\normalfont\normalsize\bfseries}}
\renewcommand{\subsubsection}{\@startsection{subsubsection}{3}{0mm}%
                                {-1ex plus -.5ex minus -.2ex}%
                                {1ex plus .2ex}%
                                {\normalfont\small\bfseries}}
\makeatother

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\setcounter{secnumdepth}{0}


\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt plus 0.5ex}

\newtheorem{example}[section]{Example}

\begin{document}
\raggedright
\footnotesize
\begin{multicols}{4}


% multicol parameters
% These lengths are set only within the two main columns
%\setlength{\columnseprule}{0.25pt}
\setlength{\premulticols}{1pt}
\setlength{\postmulticols}{1pt}
\setlength{\multicolsep}{1pt}
\setlength{\columnsep}{2pt}

\begin{center}
     \Large{qstar - Cheatsheet} \\
\end{center}

\section{Character}

\subsection{Attributes and Skills}

All Attributes and Skills start at a d4. Can be improved up to a d6, d8, d10, or d12.

The Attributes are: \emph{Might (MI)}, \emph{Speed (SP)}, \emph{Intelligence (IN)}, \emph{Charisma (CA)}.

\subsection{Stats}

\( \emph{Pace} = 2 + Speed / 2 \)

\( \emph{Perception} = 2 + Intelligence / 2 \)

\( \emph{Parry} = 2 + Melee / 2 \)

\( \emph{Toughness} = 2 + Might / 2 \)

\subsection{Health (HP)}

If Health drops to 0 or below, make a Might roll. On failure become \emph{incapacitated} until healed or dead.

If Health drops to its negative maximum, the character dies.

\( \emph{Health} = 2 + Might / 4 \)

\subsection{Experience (XP)}

Three XP is a level up.

Usually one XP per sessions / missions etc.

\subsubsection{Level (LVL)}

Increases Maximum of Acquisitions.

\begin{itemize}
  \item Every Level gives 1 Skill Point.
  \item Every 2 Levels gives 1 Attribute Point.
  \item Every 4 Levels give a Talent.
\end{itemize}

\subsection{Fate}

Every character has a d4, d6, d8, d10, d12, that can be used on any roll.

Has to be used before rolling, and can only be used once in a character's lifetime.

Multiple dice can be used at once too.

\subsection{Acquisition}

Abstracts resources available to a character.

Every Acquisition has a Maximum value that cannot be exceeded.

\subsubsection{Loot (LOOT)}

Gained from looting enemies. It's worth 1000 Credits.

\emph{No Maximum, but each 1 Loot takes up 1 Bulk}.

\subsubsection{Downtime (DT)}

\( Maximum = 10 \)

\subsubsection{Influence (INF)}

\( Maximum = XP + 2 \)

\subsubsection{Resources (RES)}

\( Maximum = XP + 2 \)

\subsubsection{Technology (TECH)}

\( Maximum = XP + 2 \)

\section{Crisis}

\subsection{Difficulty}

Task difficulty is always 4. Only the roll is modified, not the task.

\subsection{Turns}

Each creature has one turn per round. Order is determiend by turn order.

\subsubsection{Turn Order}

Roll Turn Order. On a tie, roll again to resolve the tie. Keep the original roll's result.

\( Turn Order = Speed \)

\subsubsection{Action Points (AP)}

Every Action requires AP.

At the start of a turn gain 4 AP. You can never have more than 6 AP.
If an Action costs more AP than you have, you can't use it.

Actions with an AP cost higher than 6 have to be executed over multiple subsequent turns.

\subsubsection{Surprise Round}

If enemy has not noticed you and is not combat ready you gain an additional turn before the combat starts.

\subsection{Actions}

\begin{tabular}{lll}
\textbf{Action} & \textbf{AP} & \textbf{Description} \\
Attack & 2  & Attack with \emph{normal} weapon.\\
Hide   & 3  & Hide from others. \\
Move   & 1  & Move up to Pace in meters. \\
Overwatch & - & Delay turn. \\
Take Aim & 2 & +1 (+2) Bonus on Ranged Atk. \\
Sneak & 1 & Sneak up to half the Pace. \\
Stand up & 1 & Stand up when prone. \\
Use Item & 2 & Use item. AP varies. \\
\end{tabular}

\subsection{Conditions}

\begin{tabular}{lll}
\textbf{Condition} & \textbf{Description} \\
Drunk & -1 penalty on all Tasks.  \\
Exhausted & Regain only 2 AP / Turn. \\
Prone & Can't melee Atk. Cover vs Ranged. \\
Slowed & Pace halfed. \\
Stunned & Can't act, does not regain AP. \\
\end{tabular}

\subsection{Attacks}

Task roll using the weapon's associated Skill.

\subsubsection{Melee Attacks}

Attack roll has to beat target's Parry.

\subsubsection{Ranged Attacks}

Attack roll has to beat 4. Influenced by range, visibility, etc.

\subsection{Parry}

Every additional enemy in melee range reduces Parry by 1, to a minimum of 2.

\subsection{Cover}

\begin{tabular}{ll}
\textbf{Modifier} & \textbf{Condition} \\
+1 & Cover \\
+2 & Heavy Cover \\
unhittable & Total Cover
\end{tabular}

\subsection{Wounds}

See Health (HP).

Every wound imposes a -1 penalty on all Tasks.
NPCs die when they reach 0 Health.

\subsection{Healing}

\subsubsection{Natural Healing}

\section{Movement}

Movement is done in a round by spending speed points. If a character has
no more speed points left, he can take a full round to regain speed points.

\begin{center}
\begin{tabular}{ll}
Movement                     & Cost             \\
Moving                       & 1 per metre      \\
Running                      & 1 per two metres \\
Jumping                      & 2 per metres     \\
Jumping (running head start) & 1 per metre      \\
Crawling                     & 2 per metre      \\
Climbing                     & 3 per metre      \\
Change combat stance         & 1                \\
Recover from prone           & 2
\end{tabular}
\end{center}

\emph{Difficult terrain} (stairs, snow, mud, slippery surfaces) doubles the
cost. Effort can be used in stead, or to complement speed points.

\section{Skills}

Activation cost is 1 for normal skills, and 10 for special skills.
Unactivated skill may only use negative ability modifiers.

\( 1d10 + MOD1 + MOD2 + RANK + Morale \)

The result must exceed or be equal to the DC.

\begin{center}
  \begin{tabular}{llll}
\textbf{Name}             & \textbf{Ability} &  \textbf{Ability} &  \\
Acrobatics                & DEX          & CON          &  \\
Acting                    & CHA          & INT          &  \\
Climbing                  & STR          & CON          &  \\
Dodging                   & DEX          & PER          &  \\
Driving                   & PER          & DEX          &  \\
\textit{Engineering}      & \textit{INT} & \textit{INT} &  \\
Escape Artist             & STR          & DEX          &  \\
Explosives                & INT          & DEX          &  \\
First Aid                 & INT          & PER          &  \\
Heavy Weapons             & DEX          & PER          &  \\
Intrusion                 & DEX          & INT          &  \\
Language                  & PER          & INT          &  \\
Light Weapons             & PER          & DEX          &  \\
Mechanics                 & DEX          & INT          &  \\
\textit{Medicine}         & \textit{PER} & \textit{INT} &  \\
Melee Combat              & DEX          & STR          &  \\
Micro Gravity             & DEX          & STR          &  \\
Navigation                & INT          & PER          &  \\
Notice                    & PER          & INT          &  \\
Oratory                   & INT          & CHA          &  \\
\textit{Pilot Spacecraft} & \textit{DEX} & \textit{PER} &  \\
Public Affairs            & INT          & CHA          &  \\
Questioning               & INT          & CHA          &  \\
Radio Operations          & INT          & CHA          &  \\
Running                   & STR          & CON          &  \\
\textit{Science (Any)}    & \textit{INT} & \textit{INT} &  \\
Sleight of Hand           & DEX          & CHA          &  \\
Small Arms                & PER          & DEX          &  \\
Small Unit Tactics        & INT          & PER          &  \\
Stealth                   & DEX          & INT          &  \\
Swimming                  & STR          & CON          &  \\
Throwing                  & STR          & DEX          &
  \end{tabular}
\end{center}

\section{Initiative}

\(Initiative = 1d10 + DEX Mod + Morale\)

\section{Ranged Combat}

Single shot:

\( DC = 5 + Range Penalty + Movement + Stance \)

Each additional shot adds recoil penalty.

\subsection{Stance}

\begin{center}
\begin{tabular}{llll}
\textbf{Standing} & \textbf{Kneeling} & \textbf{Firing} & \textbf{Prone} \\
-1                & -2                & -3              & +2
\end{tabular}
\end{center}

\subsection{Movement}

\begin{tabular}{llll}
\textbf{Still} & \textbf{Subtle} & \textbf{Slow} & \textbf{Fast} \\
-2             & 0               & +2            & +4
\end{tabular}

\subsection{Range}

\(Maximum = \frac{effective}{2} <= range \)
\(Far = \frac{effective}{4} < range < \frac{effective}{2} \)
\(Medium = \frac{effective}{8} < range < \frac{effective}{4} \)
\(Close = effective < \frac{effective}{8} \)

\begin{center}
  \begin{tabular}{lllll}
                & \textbf{Close} & \textbf{Medium} & \textbf{Far} & \textbf{Max.} \\
\textbf{Tiny}   & +3             & +6              & +12          & +18           \\
\textbf{Small}  & +2             & +4              & +8           & +12           \\
\textbf{Medium} & +1             & +2              & +4           & +6            \\
\textbf{Large}  & -12            & -8              & -4           & -2            \\
\textbf{Huge}   & -18            & -12             & -6           & -3
\end{tabular}
\end{center}

\subsection{Misc.}

\begin{center}
\begin{tabularx}{\textwidth}{llXp{2.5cm}}
\textbf{Action}     & \textbf{Bonus} & \textbf{Time} \\
Aiming              & -2 DC          & 1 action      \\
Clear minor fault   &                & 1 action      \\
Drawing (holster)   &                & 1 action      \\
Drawing (inventory) &                & 2 actions     \\
Hiding              & -5 on stealth  &               \\
Reloading           &                & $>$ 1 action
\end{tabularx}
\end{center}

Aiming bonus to DC is lost is lost unless the shot is fired in the same round.
Reload time may vary from weapon to weapon.

\section{Melee Combat}

\subsection{Attack}

\(1d10 + Melee Combat + STR Mod + DEX Mod \)

\subsection{Dodge}

\(1d10 + Dodging + DEX Mod + PER Mod \)

This value has to be greater than the attack.

If the defender is flat footed (not aware of the action) he may not dodge. If
the defender has no more action left he takes a cumulative -2 penalty on each
additional dodge attempt.

\subsection{Blocking}

\(1d10 + CON Mod + STR Mod \)

This value has to be greater than the attack. If blocking is successful then
the damage is halved.

\section{Damage}

\subsection{Recover HP}

Recovering HP with \emph{Medicine}:

\(DC = \frac{HP Lost}{2} \)

Recovering HP with \emph{First Aid}:

\(DC = HP Lost\)

This DC is used for diagnosis and then for treatment. First, diagnose to
determine if the difference of your roll and your DC gives you a bonus to
your treatment or a penalty.

Then treat the damage with the same DC, but add (or subtract) the diagnose
penalty or bonus:

\(1d10 + Medicine + PER Mod + INT Mod + Diagnose Bonus\)

\subsection{Death}

Your character is dead if his hit points are at negative maximum hit points
minus any suffered wounds.

\(Death = HP <= ((Maximum HP - Wounds) * -1)\)

\subsection{Staying Conscious}

If your hit points drop below zero you have to roll if you remain conscious.

\(DC = abs(Damage Below 0)\)

\subsection{Wounds}

On taking damage the character rolls to see if he sustains a wound.

\(DC = Damage Taken \)

The damage taken after armour, but before any zone multipliers is the DC
for the check. On failure, the character takes one wound damage, which
lowers his maximum HP. Wounds stack with each other.

Recovering wounds works the same as recovering HP, except that the wound
total is used instead of the HP lost. See above for further information.

\section{States}

\begin{center}
\begin{tabularx}{\textwidth}{lp{4cm}}
\textbf{State}     & \textbf{Penalty}                                      \\
Blinded            & Cannot use PER mod or rank, +1 speed for all movement \\
Deafened           & Cannot use PER mod or rank                            \\
Nauseated          & -1 penalty on skill checks                            \\
Sickened           & Depends on sickness                                   \\
Stunned            & Cannot take actions or move                           \\
Unconscious        & Is considered still, cannot move or take actions
\end{tabularx}
\end{center}

If the character is \emph{blinded} and \emph{deafened} at the same time, the
perception rank is considered to be at 1 (-4 modifier).

\subsection{Default Hitzones}

\begin{center}
\begin{tabular}{lll}
\textbf{2d6} & \textbf{Zone} & \textbf{Effect}     \\
2               & Vital Organ   & Damage * 6, Special \\
3, 4            & Legs          &                     \\
5, 6, 7         & Torso         & Damage * 2          \\
8, 9            & Arms          &                     \\
10, 11          & Head          & Damage * 3          \\
12              & Vital Organ   & Damage * 6, Special
\end{tabular}
\end{center}

\section{Morale}

Morale ranges from -3 to +3. With -3 being despair, 0 being neutral and
+3 being an almost religious like frenzy to achieve the goal. Normally it is
at 0. It is used as a bonus or penalty on all checks.

To raise moral use \emph{Oratory} against the following DC:

\(DC = 5 + abs(Morale)\)

\newpage

\section{Vessels}

All vessels have \emph{hit points}, \emph{armour} which acts as damage
reduction for incoming damage, \emph{shields} which soak up damage before
it is depleted, and speed. At zero the ship is considered disabled, and at
minus HP it is considered destroyed.

Ships also have modules (these are subsystems such as engines), and the
module hit points are - unless otherwise specified, dependent on the size
and the HP for the ship:

Small: \(SubsystemHP = \frac{ShipHP}{2} \)

Medium: \(SubsystemHP = \frac{ShipHP}{4} \)

Large: \(SubsystemHP = \frac{ShipHP}{8} \)

Capital: \(SubsystemHP = \frac{ShipHP}{12} \)

Armour and shield apply to modules as well, and modules are considered destroyed
at minus their HP, and disabled at zero (0) HP. Modules at zero HP are disabled
and no longer work, and the cockpit or bridge may transfer damage to crew.

Ships also has a type, which denotes which environments in can operate in:

\begin{center}
\begin{tabular}{ll}
\textbf{Type}  & \textbf{Environment} \\
Space & Can fly in out space  \\
Air   & Can fly in atmosphere \\
Land  & Moves on land         \\
Water & Moves in or on water
\end{tabular}
\end{center}

\subsection{Sizes}

Size of the ship determines average hit points, and crew required to operate
the vessel.

\begin{center}
\begin{tabular}{lll}
\textbf{Size} & \textbf{Crew} & \textbf{HP}      \\
Small         & 5-10          & 100              \\
Medium        & 10-50         & 500              \\
Large         & 100           & \textgreater1000 \\
Capital       & 500           & \textgreater5000
\end{tabular}
\end{center}

\subsection{Combat}

Dog fights are handled by pitching \emph{Pilot Spacecraft} skill against the
opponents \emph{Pilot Spacecraft} skill. Speed of the vessel is added to the
roll.

Long ranged combat works just as normal long ranged combat, except that
\emph{Heavy Weapons} or \emph{Piloting} is used instead. All weapons have
effective range and the same rules apply as above.

Then roll against the hit table of the vessel to determine where the attack
landed.

\begin{tabular}{llll}
\textbf{Still} & \textbf{Subtle} & \textbf{Slow} & \textbf{Fast} \\
-2             & 0               & +2            & +4
\end{tabular}

\(Maximum = \frac{effective}{2} <= range \)
\(Far = \frac{effective}{4} < range < \frac{effective}{2} \)
\(Medium = \frac{effective}{8} < range < \frac{effective}{4} \)
\(Close = effective < \frac{effective}{8} \)

\begin{center}
  \begin{tabular}{lllll}
                & \textbf{Close} & \textbf{Medium} & \textbf{Far} & \textbf{Max.} \\
\textbf{Tiny}   & +3             & +6              & +12          & +18           \\
\textbf{Small}  & +2             & +4              & +8           & +12           \\
\textbf{Medium} & +1             & +2              & +4           & +6            \\
\textbf{Large}  & -12            & -8              & -4           & -2            \\
\textbf{Huge}   & -18            & -12             & -6           & -3
\end{tabular}
\end{center}

\subsection{Missiles}

Guided missiles are treated as their own (small) vehicle, with piloting skill
and speed. Point defence may be used to shoot them down. Missiles, generally
attack twice, before running out of fuel.

\subsection{Attack Module}

You can target specific modules with the following bonuses or penalties on the
DC to hit:

\begin{center}
\begin{tabular}{lllll}
                 & \textbf{Small} & \textbf{Medium} & \textbf{Large} & \textbf{Capital} \\
\textbf{Small}   & +2             & 0               & -2             & -4               \\
\textbf{Medium}  & +4             & +2              & 0              & -2               \\
\textbf{Large}   & +6             & +4              & +2             & 0                \\
\textbf{Capital} & +8             & +6              & +4             & +2
\end{tabular}
\end{center}

\subsection{Secondary Explosions}

If certain modules are destroyed, they cause explosions and thus secondary
damage to the ship.

\emph{Sublight Engines}, \emph{Shield Generators} and \emph{FTL}:

\begin{center}\begin{tabular}{ll}
\textbf{Size} & \textbf{Damage} \\
Small         & 5               \\
Medium        & 20              \\
Large         & 50              \\
Capital       & 100
\end{tabular}
\end{center}

\emph{Power Core}:

\begin{center}\begin{tabular}{ll}
\textbf{Size} & \textbf{Damage} \\
Small         & 10              \\
Medium        & 50              \\
Large         & 100             \\
Capital       & 250
\end{tabular}
\end{center}


% You can even have references
\rule{0.3\linewidth}{0.25pt}
\scriptsize
\bibliographystyle{abstract}
\bibliography{refFile}
\end{multicols}
\end{document}
